Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}

### 2021-03-22 inst/skeleton/ms.Rmd
Incorporate other smart suggestions by @andrewheiss to simplify the table-rendering chunk.

if (is_latex) {
  tab_reg %>%
  row_spec(0, bold=TRUE) %>%
  pack_rows("The Important Stuff",1, 12) %>%
  pack_rows("Stupid Thing I Added", 13, 14)
} else if (is_docx) {
  tab_reg %>%
  set_font_size(10) %>%
  set_left_padding(1) %>%
  set_top_padding(1) %>%
  set_bottom_padding(1) %>%
  set_right_padding(1) %>%
  insert_row(., "Stupid Thing I Added", "", "", after=13) %>%
  insert_row(., "The Important Stuff","", "", after=1) %>%
  set_bold(., 1, 1:3, TRUE) %>%
  set_bold(2, 1:3, TRUE) %>%
  set_bold(15, 1:3, TRUE) %>%
  as_flextable()
} else {
  print("No other format available.")
}
```

>>>>

if (!is_docx) {
  tab_reg %>%
  row_spec(0, bold=TRUE) %>%
  pack_rows("The Important Stuff",1, 12) %>%
  pack_rows("Stupid Thing I Added", 13, 14)
} else {
  tab_reg %>%
  set_font_size(10) %>%
  set_left_padding(1) %>%
  set_top_padding(1) %>%
  set_bottom_padding(1) %>%
  set_right_padding(1) %>%
  insert_row(., "Stupid Thing I Added", "", "", after=13) %>%
  insert_row(., "The Important Stuff","", "", after=1) %>%
  set_bold(., 1, 1:3, TRUE) %>%
  set_bold(2, 1:3, TRUE) %>%
  set_bold(15, 1:3, TRUE) %>%
  as_flextable()
} 
```
